---
title: "The UPR & Maternal Health"
params:
  country_name: "Switzerland"
  upr_all: NULL
  rec_plot: NULL
  mmr_map_plot: NULL
documentclass: article
# classoption: twocolumn
output: 
  pdf_document:
    includes:
      in_header: preamble-b.tex
    keep_tex: true
    latex_engine: xelatex
geometry: 
  - top=2cm
  - bottom=0.5cm
  - left=0.2cm
  - right=0.2cm
papersize: a4
date: "2025-09-30"
---
```{r setup, include=FALSE}
# This chunk loads the necessary packages for the report
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.align='center', out.width="100%")
pacman::p_load(
  here,
  dplyr,
  ggplot2, 
  ggtext, 
  patchwork,
  sf
)

# Load or install packages from GitHub:
pacman::p_load_gh(
  "PPgp/wpp2024"
)

state_geo <- readRDS(here("output", "state_geo_enhanced.rds"))
nearest_neighbors_list <- readRDS(here("output", "nearest_neighbors_list.rds"))
iso3_SUR <- state_geo |> filter(country==params$country_name) |> pull(iso3)

# Life expectancy
data(e01dt);data(pop1dt)
life_expectancy <- e01dt |> 
  left_join(state_geo |> sf::st_drop_geometry() |> select(iso3,iso2, loc_id),
            join_by(country_code==loc_id)) |> 
  filter(
    !is.na(iso3),
    year>=2005
  );rm(e01dt)

pop_wpp <- pop1dt |> 
  left_join(state_geo |> sf::st_drop_geometry() |> select(iso3,iso2, loc_id),
            join_by(country_code==loc_id)) |> 
  filter(
    !is.na(iso3),
    year>=2005
  );rm(pop1dt)

# Loop through API-generated files
for (file_name in list.files(path = here("data", "API_data"), pattern = "\\.rds$")) {
  object_name <- gsub("\\.rds$", "", file_name)
  assign(object_name, readRDS(here("data", "API_data", file_name)))
}
```

```{r}
UHC_estimate <- UHC_all |>
  filter(IndicatorCode == "UHC_INDEX_REPORTED",
         country_name == params$country_name,
         YEAR == max(YEAR)
         )

life_expectancy_C <- life_expectancy |> 
  filter(iso3 == iso3_SUR,
         year==max(year))

pop_C <- pop_wpp |> 
  filter(iso3==iso3_SUR)
```

\maketitle
# `r params$country_name`  

Some brief text here, for context, that runs the \textcolor{CeHDIRed}{entire width of the page}. Indicator results, tables, and figures can go into the columns below.

```{r, out.width="30%", warning=FALSE}
p1<-UHC_all |> 
  filter(country_name == params$country_name, 
         IndicatorCode == "UHC_INDEX_REPORTED") |>
  ggplot(aes(x = YEAR, y= NumericValue))+geom_line()+
  theme_void()

HPV_coverage_C <- HPV_coverage |> filter(SpatialDim==iso3_SUR)
adolescent_birth_rate_C <- adolescent_birth_rate |> filter(SpatialDim==iso3_SUR) |> filter(YEAR == max(YEAR))
contraceptive_prevalence_C <- contraceptive_prevalence |> filter(SpatialDim==iso3_SUR) |> filter(YEAR==max(YEAR))
```

\textcolor{fgcolor}{\textbf{\hlCeHDIRed{At a glance:}}}  

***Population***: `r round(pop_C |> filter(year==max(year)) |> pull(pop)/1000,1)`  million in `r pop_C |> filter(year==max(year)) |> pull(year)` (`r (round(pop_C |> filter(year==max(year)) |> pull(pop)/pop_C |> filter(year==min(year)) |> pull(pop),1)-1)*100`% growth since `r pop_C |> filter(year==min(year)) |> pull(year)`)

***Key Health Indicators***  
<!-- Maternal Mortality Ratio:   -->
<!-- Under-Five Mortality Rate   -->
Adolescent Birth Rate (aged 10-14):  `r adolescent_birth_rate_C |> filter(Dim2=="AGEGROUP_YEARS10-14") |> pull(Value)` per 1,000 women  
Adolescent Birth Rate (aged 15-19):  `r adolescent_birth_rate_C |> filter(Dim2=="AGEGROUP_YEARS15-19") |> pull(Value)` per 1,000 women  
Contraceptive Prevalence Rate:  `r contraceptive_prevalence_C |> pull(Value)`  
HPV Immunization Coverage (9-14 year old girls):  `r HPV_coverage_C |> filter(YEAR == max(YEAR)) |> pull(NumericValue)`% in `r HPV_coverage_C |> filter(YEAR == max(YEAR)) |> pull(YEAR)`  
\textcolor{fgcolor}{\hlCeHDIBlue{UHC service coverage index:}} `r UHC_estimate |> pull(NumericValue)` in `r UHC_estimate |> pull(YEAR)`  
\textcolor{fgcolor}{\hlCeHDIBlue{Life expectancy at birth:}} `r life_expectancy_C |> pull(e0B) |> round(1)` years in `r life_expectancy_C |> pull(year)`

<!-- \textcolor{fgcolor}{\hlCeHDIBlue{colortest}} -->
<!-- \textcolor{fgcolor}{\textbf{\hlCeHDIBlue{colortest}}} -->
<!-- \textcolor{fgcolor}{\hlCeHDIRed{colortest}} -->
<!-- \textcolor{fgcolor}{\textbf{\hlCeHDIRed{colortest}}} -->

\redrule
```{=latex}
\begin{multicols}{2}
\raggedcolumns     %new code
\interlinepenalty=10000
```

This plot shows all health-related recommendations received by the selected state across all UPR cycles.

```{r, fig.width=6, fig.height=5.5}
print(params$upr_all+
        theme(
          axis.title.x = element_text(color = "black"),
          plot.background = element_rect(color = "#1c164d", fill = NA),
          panel.background = element_blank(),
          legend.background = element_blank()
        )
)
```

```{r, fig.width=4, fig.height=3.5}
print(
  params$rec_plot+
    labs(y="Recommendations (N)")+
    geom_text(aes(label = sprintf("%1.0f", n_tot), y = n_tot, vjust = -0.2), size = 5, fontface = "bold", color = "#1c164d") +
    theme(
      panel.grid = element_blank(),
      axis.text.x = element_text(size = 12, color = "#1c164d"),
      axis.text.y = element_text(size = 12, color = "#1c164d"),
      axis.title.x = element_blank(),
      axis.title.y = element_text(size = 14, color = "#1c164d"),
      legend.position = "bottom",
      # legend.position = c(0.01, 0.99),
      # legend.justification = c("left", "top"),
      legend.text = element_text(size = 12,colour = "#1c164d"),
      # plot.background = element_blank(),
      plot.background = element_rect(color = "#1c164d", fill = NA),
      panel.border = element_rect(color = "#1c164d"),
      # panel.border = element_blank(),
      axis.ticks = element_line(color = "#1c164d"),
      panel.background = element_blank(),
      legend.background = element_blank(),
      strip.background = element_blank(),
      strip.text = element_blank(),
      plot.title = element_blank()
    )
)
```

```{r, fig.width=6}
print(
  params$mmr_map_plot
  # params$mmr_map_plot+theme(
  #   plot.background = element_blank()
  # )&
  # plot_annotation(theme = theme(
  #   plot.background = element_rect(color = "#1c164d", fill=NA)
  #   )
  #   )
)
```


<!-- ```{r, fig.height=3, out.width="80%"} -->
<!-- penguins |> ggplot(aes(x = island, y = bill_len, fill=species))+geom_violin() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- penguins |> ggplot(aes(x = island, y = bill_len, fill=species))+geom_boxplot() -->
<!-- ``` -->

<!-- ```{r, fig.height=3, out.width="80%"} -->
<!-- penguins |> ggplot(aes(x = island, y = bill_len, fill=species))+geom_violin() -->
<!-- ``` -->

<!-- ```{r, fig.width=3, out.height="500pt", } -->
<!-- penguins |> ggplot(aes(x = island, y = bill_len, fill=species))+geom_boxplot() -->
<!-- ``` -->

<!-- ```{r, fig.height=3, out.width="80%"} -->
<!-- penguins |> ggplot(aes(x = island, y = bill_len, fill=species))+geom_violin() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- penguins |> ggplot(aes(x = island, y = bill_len, fill=species))+geom_boxplot() -->
<!-- ``` -->

<!-- ```{r, fig.height=3, out.width="80%"} -->
<!-- penguins |> ggplot(aes(x = island, y = bill_len, fill=species))+geom_violin() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- penguins |> ggplot(aes(x = island, y = bill_len, fill=species))+geom_boxplot() -->
<!-- ``` -->

```{=latex}
\end{multicols}
```